**Density Dependence**

### 2023-02-09 Rmd/ddMac.Rmd
fixed ssb issue

lsr=landings.wt(eq)/stock.wt(eq)
dsr=discards.wt(eq)/stock.wt(eq)
# iterate
for (i in seq(10)){
  stock.wt(   x)=ddWt(stock.wt(eq),biomass(x),refpts(eq)["msy","biomass"],alpha=-0.17)
  landings.wt(x)=stock.wt(x)*lsr
  discards.wt(x)=stock.wt(x)*dsr
  x=brp(x)}

ggplot()+
  geom_line(aes(ssb,catch),
            data=model.frame(FLQuants(x, ssb=function(x) ssb(x), catch=function(x) catch(x)),drop=T))+
  geom_line(aes(ssb,catch),
            data=model.frame(FLQuants(eq,ssb=function(x) ssb(x), catch=function(x) catch(x)),drop=T),col="red")+
  xlab("SSB")+ylab("Catch")
```

@@

lsr=landings.wt(eq)/stock.wt(eq)
dsr=discards.wt(eq)/stock.wt(eq)
# iterate
for (i in seq(10)){
  stock.wt(   x)=ddWt(stock.wt(eq),biomass(x),refpts(eq)["msy","biomass"],alpha=-0.17)
  landings.wt(x)=stock.wt(x)*lsr
  discards.wt(x)=stock.wt(x)*dsr

@@

ggplot()+
  geom_line(aes(ssb,catch),
            data=model.frame(FLQuants(x, ssb=function(x) ssb(x), catch=function(x) catch(x)),drop=T))+
  geom_line(aes(ssb,catch),
            data=model.frame(FLQuants(eq,ssb=function(x) ssb(x), catch=function(x) catch(x)),drop=T),col="red")+
  xlab("SSB")+ylab("Catch")
```

@@

```{r, check1}
par=FLPar(c(m1=0.2/(300^-0.288),m2=-0.28,bmsy=c(refpts(eq)["msy","ssb"]),k=0.1,w50=par["a"]*par["l50"]^par["b"]))

f=FLQuant(c(rep(seq(0,1,length.out=101),each=51),rep(seq(1,5,length.out=101),each=51)[-1]),
          dimnames=list(year=dimnames(om)$year,iter=seq(101)))%*%refpts(eq)["msy","harvest"]
fbar(eq)=f

@@

  om2=ddFn(year,om2,par)}

catch(om2)=computeCatch(om2,slot="all")
plot(window(FLStocks("OM"=om,DD=om2),start=11))
```

@@

```{r, check2}
save(om2,file="~/Desktop/tmp/t.RData")
load("~/Desktop/tmp/t.RData")
ggplot(model.frame(FLQuants(om2[,dim(m(om2))[2]],"Biomass"=biomass,"Yield"=catch)))+
  geom_line(aes(Biomass,Yield),col="red")+
  geom_line(aes(Biomass,Yield),data=model.frame(FLQuants(om[,dim(m(om))[2]],"Biomass"=biomass,"Yield"=catch)))
```

>>>>

lsr=landings.wt(eq)/stock.wt(eq)
dsr=discards.wt(eq)/stock.wt(eq)
# iterate
for (i in seq(10)){
  stock.wt(   x)=ddWt(stock.wt(eq),biomass(x),refpts(eq)["msy","biomass"],alpha=-0.2)
  landings.wt(x)=stock.wt(x)*lsr
  discards.wt(x)=stock.wt(x)*dsr
  x=brp(x)}

ggplot()+
  geom_line(aes(biomass,catch),
            data=model.frame(FLQuants(x, biomass=function(x) biomass(x), catch=function(x) catch(x)),drop=T))+
  geom_line(aes(biomass,catch),
            data=model.frame(FLQuants(eq,biomass=function(x) biomass(x), catch=function(x) catch(x)),drop=T),col="red")+
  xlab("SSB")+ylab("Catch")
```

@@

lsr=landings.wt(eq)/stock.wt(eq)
dsr=discards.wt(eq)/stock.wt(eq)
# iterate
for (i in seq(10)){
  stock.wt(   x)=ddWt(stock.wt(eq),biomass(x),refpts(eq)["msy","biomass"],alpha=-0.2)
  landings.wt(x)=stock.wt(x)*lsr
  discards.wt(x)=stock.wt(x)*dsr

@@

ggplot()+
  geom_line(aes(biomass,catch),
            data=model.frame(FLQuants(x, biomass=function(x) biomass(x), catch=function(x) catch(x)),drop=T))+
  geom_line(aes(biomass,catch),
            data=model.frame(FLQuants(eq,biomass=function(x) biomass(x), catch=function(x) catch(x)),drop=T),col="red")+
  xlab("SSB")+ylab("Catch")
```

@@

```{r, check1}
par=FLPar(c(m1=0.2/(300^-0.288),m2=-0.28,bmsy=c(refpts(eq)["msy","biomass"]),k=0.1,w50=par["a"]*par["l50"]^par["b"]))

f=FLQuant(c(rep(seq(0,1,length.out=51),each=101),rep(seq(1,25,length.out=61)[-1],each=101)),
          dimnames=list(year=dimnames(om)$year,iter=seq(101)))%*%refpts(eq)["msy","harvest"]
fbar(eq)=f

@@

  om2=ddFn(year,om2,par)
  om2=fwd(om2,f=f[,year],sr=eq)
  }

catch(om2)=computeCatch(om2,slot="all")
plot(window(FLStocks("OM"=om,DD=om2),start=400))
```

@@

```{r, check2} 
ggplot(model.frame(FLQuants(om2[,dim(m(om2))[2]],"Biomass"=biomass,"Yield"=catch)))+  
  geom_line(aes(Biomass,Yield),col="black")+ 
  geom_line(aes(Biomass,Yield),data=model.frame(FLQuants(om[,dim(m(om))[2]],"Biomass"=biomass,"Yield"=catch)),col="red")
```
